An interactive exploration of how changes in cause of death have narrowed the

### 2017-04-17 ResearchDay/Riddell_ResearchDay.Rmd

@@

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
```

@@

```{r plot_LE_trends_males, echo=F, fig.height=9, fig.width=11, out.height="80%"}
LE_trend_plot_males +
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 15), lwd = 0.5, col = "grey", alpha = 0.5)

@@

```{r, echo=F}
library(png)
library(jpeg)
library(grid)
library(gridExtra)
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img1,
             img2,
             img3,
             ncol = 3)
```

@@

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Kathryn Morrison, PhD"}
knitr::include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/k_morrison.png")
```

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Sam Harper, PhD"}
knitr::include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/s_harper.jpeg")
```

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Jay Kaufman, PhD"}
knitr::include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/j_kaufman.jpg")
```

>>>>

library(png)
library(jpeg)
library(grid)
library(gridExtra)
library(knitr)

@@

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map(BlackWhite_results, "state", "stabbrs")

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")
```

@@

```{r plot_LE_trends_males, echo=F, fig.height=9, fig.width=11, out.height="90%", out.width = "90%"}
LE_trend_plot_males <- LE_trend_plot_males + 
  geom_hline(aes(yintercept = 0), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 5), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 10), lwd = 0.5, col = "grey", alpha = 0.5) +
  geom_hline(aes(yintercept = 15), lwd = 0.5, col = "grey", alpha = 0.5)

refine.patterns <- function(plot) {
  for(i in 1:240){
  if(plot$x$data[[i]]$line$color == "rgba(190,190,190,1)"){
    plot$x$data[[i]]$line$width <- 0.7559055
    plot$x$data[[i]]$hoverinfo <- "none"
  }
    if(plot$x$data[[i]]$line$color == "rgba(0, 0, 0, 1)"){
    plot$x$data[[i]]$hoverinfo <- "none"
  }
  }
  return(plot)
}

LE_trend_plot_males2 <- refine.patterns(ggplotly(LE_trend_plot_males))

LE_trend_plot_males2

@@

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img1,
             img2,
             img3,
             ncol = 3)
```

@@

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Kathryn Morrison, PhD"}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/k_morrison.png")
```

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Sam Harper, PhD"}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/s_harper.jpeg")
```

```{r, echo=F, out.width="15%", dpi=72, fig.cap="Jay Kaufman, PhD"}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/ResearchDay/images/j_kaufman.jpg")
```
